High-accuracy neutron diffusion calculations based on integral transport theory

### 2019-12-05 docs/EPJP2019/Gross-EPJP-2019.tex
Minor changes to abstract and introduction
Changed iterative calculations of the diffusion coefficient - TO: diffusion correction factors.

%
\graphicspath{ {./figures/} }
% ---------------------------------------------------
\begin{document}
%
\title{High-accuracy neutron diffusion calculations based on integral transport theory}
%\subtitle{}
\author{
	Roy Gross\inst{1} \and 
	Daniele Tomatis\inst{2} \and 
	Erez Gilad\inst{1}\thanks{\email{gilade@bgu.ac.il} (corresponding author)}
}                     % Do not remove
%
%\offprints{}          % Insert a name or remove this line
%
\institute{
	The Unit of Nuclear Engineering, Ben-Gurion University of the Negev, 8410501 Beer-Sheva, Israel 
	\and
	CEA, DEN, Service d'{\'e}tudes des r\'eacteurs et de math\'ematiques appliqu\'ees (SERMA),
	Universit\'e Paris-Saclay, F-91191 Gif-sur-Yvette, France}
%
\authorrunning{Gross, Tomatis \& Gilad} 
\titlerunning{Integral transport correction to diffusion calculations}
\date{Received: date / Revised version: date}
% The correct dates will be entered by Springer
%
\abstract{
In this paper, the Ronen method is developed, implemented, and applied to resolve the neutron flux and the criticality eigenvalue in one-dimensional simple homogeneous problem and in more complex heterogeneous benchmarks. The Ronen method is based on iterative calculations of the multigroup diffusion coefficients using a multigroup diffusion model and is driven by the solutions of the integral transport equation. The spatially-dependent diffusion constants are modified locally in order to produce new estimates of the surface currents using an integral transport expression. The diffusion solver employed in this study uses finite differences and the transport-corrected currents are introduced into the numerical scheme using drift terms. The corrected solutions are compared against reference results obtained by a discrete ordinate code. Boundary conditions are discussed and proper approximations are introduced to conserve the particle balance. The results match well with the reference solutions, especially in the limit of fine meshes, but slow convergence of the scalar flux is reported.
% 
\PACS{
	{28.00.00}{Nuclear engineering and nuclear power studies} \and
	{28.20.Gd}{Neutron transport: diffusion and moderation} \and
	{05.60.-k}{Transport processes} \and
	{28.41.-i}{Fission reactors}
     } % end of PACS codes
  \keywords{
  	neutron diffusion -- integral transport -- non-linear transport correction
  }
} %end of abstract
%
\maketitle
%
% ---------------------------------------------------
\section{Introduction}
\label{sec:intro}

@@

A crucial issue in obtaining an accurate diffusion calculation is the formulation of the diffusion coefficient~\cite{Bell-1970,Pounders-2009}. The calculation of this parameter should be based on physical insights from the transport equation such that the resulting improved ("transport corrected") diffusion approximation can capture the transport phenomena of interest. Such transport corrections can be divided into two main classes. The first class is based on extending the $P_1$ model equations (and the associated boundary conditions) along with some closure scheme, such as the well-known $SP_3$ approximation~\cite{Brantley-2000}. The second class, to which this study belongs, is based on the re-calculation of the diffusion coefficients within the multigroup diffusion framework~\cite{Tomatis-2011}.

>>>>

%
\graphicspath{ {./figures/} }
% ---------------------------------------------------
\begin{document}
%
\title{High-accuracy neutron diffusion calculations based on integral transport theory}
%\subtitle{}
\author{
	Roy Gross\inst{1} \and 
	Daniele Tomatis\inst{2} \and 
	Erez Gilad\inst{1}\thanks{\email{gilade@bgu.ac.il} (corresponding author)}
}                     % Do not remove
%
%\offprints{}          % Insert a name or remove this line
%
\institute{
	The Unit of Nuclear Engineering, Ben-Gurion University of the Negev, 8410501 Beer-Sheva, Israel 
	\and
	CEA, DEN, Service d'{\'e}tudes des r\'eacteurs et de math\'ematiques appliqu\'ees (SERMA),
	Universit\'e Paris-Saclay, F-91191 Gif-sur-Yvette, France}
%
\authorrunning{Gross, Tomatis \& Gilad} 
\titlerunning{Integral transport correction to diffusion calculations}
\date{Received: date / Revised version: date}
% The correct dates will be entered by Springer
%
\abstract{
In this paper, the Ronen method is developed, implemented, and applied to resolve the neutron flux and the criticality eigenvalue in one-dimensional simple homogeneous problem and in more complex heterogeneous benchmarks. The Ronen method is based on iterative calculations of the multigroup diffusion correction factors using a multigroup diffusion model and is driven by the solutions of the integral transport equation. The spatially-dependent diffusion constants are modified locally in order to produce new estimates of the surface currents using an integral transport expression. The diffusion solver employed in this study uses finite differences and the transport-corrected currents are introduced into the numerical scheme using drift terms. The corrected solutions are compared against reference results obtained by a discrete ordinate code. Boundary conditions are discussed and proper approximations are introduced to conserve the particle balance. The results match well with the reference solutions, especially in the limit of fine meshes, but slow convergence of the scalar flux is reported.
% 
\PACS{
	{28.00.00}{Nuclear engineering and nuclear power studies} \and
	{28.20.Gd}{Neutron transport: diffusion and moderation} \and
	{05.60.-k}{Transport processes} \and
	{28.41.-i}{Fission reactors}
     } % end of PACS codes
  \keywords{
  	neutron diffusion -- integral transport -- non-linear transport correction
  }
} %end of abstract
%
\maketitle
%
% ---------------------------------------------------
\section{Introduction}
\label{sec:intro}

@@

A crucial issue in obtaining an accurate diffusion calculation is the formulation of the diffusion coefficient~\cite{Bell-1970,Pounders-2009}. The calculation of this parameter should be based on physical insights from the transport equation such that the resulting improved ("transport corrected") diffusion approximation can capture the transport phenomena of interest. Such transport corrections can be divided into two main classes. The first class is based on extending the $P_1$ model equations (and the associated boundary conditions) along with some closure scheme, such as the well-known $SP_3$ approximation~\cite{Brantley-2000}. The second class, to which this study belongs, is based on the re-calculation of the diffusion correction factors within the multigroup diffusion framework~\cite{Tomatis-2011}.
